%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% viridis959 - resume
% LaTeX Template
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by default.
% If you get compilation errors saying a font is missing, find the line on
% which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{resume}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\rfoot{Page \thepage \hspace{1pt}}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Samuel}{Luo}{I am a software engineer focusing on backend development, \\
having enthusiasm for researching the latest technology.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.3\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     INFO
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{INFO}
Phone: 0978-827-795 \\
Email: viridis959@gmail.com \\
Github: \href{https://github.com/viridis959}{\underline{viridis959}} \\
LinkedIn: \href{https://www.linkedin.com/in/samuel-luo-9b15671b5}{\underline{Samuel Luo}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{EDUCATION} 
\descript{National Chengchi University}
\descript{Management Information Systems}
\descript{Bachelor's degree}
\location{July 2017 - June 2021}
2021 Presidential Award \\
Cum. GPA: 3.66 / 4.0
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LAB
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{LABS}
\descript{MIT}
Operating System (C) \\
Database Systems (JAVA)
\sectionsep

\descript{CMU}
Intro to Computer Systems (C) \\
Distributed Systems (C \& JAVA)
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{SKILLS}
\descript{Programming Language}
Java \\ Python \\Shell \\ \LaTeX\
\sectionsep

\descript{Technologies \& Tools}
Linux \\ Spring \\ Struts2 \\ JUnit \\ 
Maven \\ RDBMS \\ Git \\ Docker \\ Kubernetes \\ 
Katalon \\ Azure Devops \\ Aliyun

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.69\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{EXPERIENCE}
\descript{WPG Holdings Limited | Backend Engieer}
\location{Aug 2021 – Present}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Large Enterprise / {\bf Scrum} Team
\item Migrated backend framework of the main website from {\bf Struts2} to {\bf Spring Boot}.
\item Researched and used features of JAVA \& Spring to improve the code. \\ 
      (POJO, Builder, Constructor Overloading, Spring Session Data Redis...)
\item Created {\bf CI / CD} pipelines to simplify deploy process. ({\bf Azure DevOps})
\item Used {\bf Docker} to containerized the main service. (JAVA \& Gradle \& Tomcat)
\item Researched and integrated {\bf Azure DevOps} with {\bf Aliyun K8s}.
\item Developed automated End-to-End testing using Katalon.
\end{tightemize}
\sectionsep

\descript{Data Yoo Application CO., Ltd. | Software Engineer Intern}
\location{Sep 2020 – Mar 2021}
\begin{tightemize}
\item Startup / Fast Pace
\item Learned and used {\bf OOP} \& {\bf design pattern} to improve the code. ({\bf Spring Boot})
\item Developed another display way of table to resolve {\bf jQuery} RWD problems.
\item Developed a new system to help debugging \& marketing.
\item Communicated with data scientists \& PM to develop LINE Bot. ({\bf Django})
\item Maintained web crawlers and developed new ones in need. ({\bf Python})
\end{tightemize}
\sectionsep

\descript{Graduation Project | Main Developer}
\location{Feb 2020 – Dec 2020}
\begin{tightemize}
\item Designed the architecture of the system. ({\bf Vue} \& {\bf Django} \& JSON)
\item Researched and introduced tools to others. (Vue CLI \& Git \& Heroku)
\item Transfered marcom's opinions to a To-Do List and refered to it for development.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SPECIAL PROJECT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{SPECIAL PROJECT}
\descript{Title}
\location{ 2021 – Present}
description
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
